---
title: "plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

this is the page about plotly 

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


nyc air bnb data

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  select(neighbourhood_group, neighbourhood, stars, price, room_type, lat, long) %>% 
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  ) %>% 
  drop_na(stars)
```

## make a scatterplot w plotly

'\n' means new line
the str_c is concactenating the things in the parnethesis together to add labels to the specified variables 

the text_label mutate funciton is making a new variable that lists price with the words Price: $ infront of it and then on a new line lists # stars w the words Rating: in front of it (that whole structure of pretext + var + spacing is contained with the variable text_label)

dont forget that you have to put tildes ~ in front of all the variable names!!!!

```{r}
nyc_airbnb %>% 
  mutate(
    text_label = str_c("Price: $", price, "\nRating:", stars)
  ) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers", color = ~price, text = ~text_label, alpha = 0.5
  )
```

## plolty boxplyto

```{r}
nyc_airbnb %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)
  ) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box",
          colors = "viridis")
```

## Bar chart

here, you are counting the number of air bnbs in each neighborhood, and then factor reordering htem in terms of this value n, and then bc its a bar plot you have to specify that you're doing count as the y axis i.e. y = ~n

this is distilling your data to only what oyu ened for a barchart

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```


## ggplotly

Jeff doesnt love it but people use it

```{r}
gg_lat_long = 
  nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

ggplotly(gg_lat_long)

```

